The Analogue Method for Precipitation Prediction: Finding Better Analogue Situations at a Sub-Daily Time Step

### 2016-12-06 Moving temporal window - HESS/template.tex
Last personnal corrections.

	\begin{abstract}
		Analogue methods (AM) predict local weather variables (predictands), such as precipitation, by means of a statistical relationship with predictors at a synoptic scale. The analogy is generally assessed on gradients of geopotential fields first, in order to sample days with a similar atmospheric circulation. Other predictors, such as moisture variables, can also be added in a successive level of analogy.

		The search for candidate situations for a given target day is usually undertaken by comparing the state of the atmosphere at fixed hours of the day for both the target day and the candidate analogues. The main reason is the use of daily precipitation time series due to the length of their available archives, and the unavailability of equivalent archives at a finer time step. However, it is unlikely for the best analogy to occur at the very same hour, while it may be found with a time shift of some hours as it may occur at a different time of day. In order to assess the potential for finding better analogues at a different hour, a moving time window (MTW) has been introduced on a reduced archive of hourly precipitation totals.

@@

		However, the MTW requires a sub-daily precipitation time series, which is generally available for a shorter period than daily precipitation archives. Therefore, two simple temporal disaggregation methods were assessed in order to make longer archives usable with the MTW. The assessed approaches were not successful, emphasizing the need to use time series with an appropriate chronology. These should be available in the near future, either by means of growing archives of measurements or by the establishment of regional precipitation reanalysis data at sub-daily time step. The use of an MTW in the AM could then be considered for any application and in any context, may it be for operational forecasting or climate-related studies.

@@

	Analogue methods (AMs) are based on the hypothesis that two relatively similar synoptic situations may produce similar local effects \citep{Lorenz1956, Lorenz1969}. They are statistical downscaling methods \citep{Maraun2010} and consist of finding past situations that are similar in terms of the atmospheric circulation or other synoptic predictors to the target day of interest. The local weather variables of interest (predictand) that were observed at the analogue dates are used to construct a probabilistic prediction for the target day \citep{Duband1970, Zorita1999}. Multiple variations of the method exist \citep[a non-exhaustive listing can be found in][]{BenDaoud2016}. The AMs are used for operational precipitation forecasting, either in the context of weather forecasting, flood forecasting, or hydropower production \citep[e.g.,][]{Guilbaud1997, Bontron2005, Hamill2006, Desaint2008a, GarciaHernandez2009b, Bliefernicht2010, Marty2010, Marty2012, Horton2012, Obled2014, Hamill2015, BenDaoud2016}, as well as in precipitation downscaling from a climate perspective \citep[e.g.][]{Radanovics2013, Chardon2014, Dayon2015}. Other applications focus on temperatures \citep{Radinovic1975, Woodcock1980, Kruizinga1983, DelleMonache2013, Caillouet2016}, wind \citep{Gordon1987, DelleMonache2013, DelleMonache2011, Vanvyve2015, Alessandrini2015, Junk2015, Junk2015c}, solar power \citep{Alessandrini2015a, Bessa2015}, snow avalanches \citep{Obled1980, Bolognesi1993}, insolation \citep{Bois1981}, and the trajectories of tropical cyclones \citep{Keenan1981, Sievers2000, Fraedrich2003}.

	The spatial transferability of the method is analysed in \citet{Chardon2014}. A great advantage of AMs is that they create realistic precipitation patterns, since they are based on observed situations with consistent spatial distribution, as long as the analogue dates chosen for a region are the same. Their temporal transferability has also been the topic of recent studies for past or future climates \citep{Dayon2015, Caillouet2016}.

@@

	Therefore, due to the availability of long precipitation archives at a daily time step that have no equivalent at a finer resolution, AMs are usually implemented on a daily basis. Therefore, the analogue situations are assessed by comparing predictors at fixed hours of the day. However, it can be expected that the analogy of the synoptic situations does not occur systematically at the same time of the day and that better candidates can be found by shifting to a different hour. With this assumption, a moving time window (MTW) was introduced to allow the search for candidates at different hours of the day. Previous tests showed the benefit, in terms of analogy criterion values, of searching for analogue synoptic situations at a finer time step, but without assessing the impact on the prediction skill \citep{Finet2008}.

@@

	Synoptic-scale variables, used as predictors, were extracted from the NCEP/NCAR reanalysis I dataset \citep{Kalnay1996} with a 6-hour temporal resolution, 17 pressure levels, and a spatial resolution of 2.5\degree. This dataset is now relatively old, but it is not expected to affect the conclusions of the present study (see discussion in Sect. \ref{sec:old_reanalysis}).

@@

	The first considered AM is based on the analogy of the atmospheric circulation only \citep[Table \ref{table:method_2Z},][]{Obled2002, Bontron2005, Marty2012}. Searching for analogue situations to a target day starts by a seasonal stratification through a preselection step of the potential candidates for analogy. The restriction is a search for analogue days within a 4-month window centred on the target date for every year of the archive. The similarity of the atmospheric circulation of the target date with every day of the preselection is assessed by processing the \citet{Teweles1954} score (S1) that is a comparison of gradients on geopotential heights over a certain spatial window and at certain hours:

@@

	The moving time window (MTW) technique aims at finding better analogue situations at different hours of the day rather than comparing the predictors at the same fixed hours. If the target situation is kept at 12 and 24~h~UTC for Z1000 and Z500 respectively, candidate situations are not only considered at 12 and 24~h~UTC, but at other hours by allowing a time shift. Therefore, instead of looking for analogues at a 24-hourly time step, they are sought at the time step matching the predictor temporal resolution which is a 6-hour time step in this study (Fig. \ref{fig:principle}).

@@

	In order to assess the benefit of searching for analogue situations at a sub-daily time step, an appropriate precipitation series is required. On the basis of high temporal resolution time series (Sect. \ref{sec:data}), 24~h-totals were processed at a 6-hour time step by means of a moving 24~h-total. Since sub-daily precipitation time series are available on a shorter period than daily ones, the loss of performance resulting from a reduction of a 47~year archive (1961 to 2008) to 25~years (1982 to 2007) can be expected. However, the competition between the loss of performance due to a smaller archive length and the potentially better analogy between target and MTW candidates needs to be assessed.

@@

	It would be profitable to be able to apply the MTW to a longer archive (here, 1961 to 2008), rather than being limited to the reduced period where the sub-daily precipitation data are available (cf. previous section). Therefore, in order to reconstruct a longer archive of moving 24~h-totals, two simple disaggregation approaches of the daily precipitation time series were assessed.

	The first technique was a proportional distribution, where the observed daily precipitations were considered constant during the measuring period (6~h~UTC to 6~h~UTC the next day). Proportional parts of the original daily time series were allocated into a new moving average of 24~h-totals (Fig. \ref{fig:illustration_disaggregation}).

@@

		\item For every level of analogy:
		\begin{enumerate}
			\item Identification of the most skilled unitary cell (one point for moisture variables and four for the geopotential height when using the S1 criterion) over a large domain. Every point (or cell) of the full domain is assessed on all predictors of the level of analogy, jointly (consisting generally of the same variable but on different pressure levels and at different hours).
			\item From this most skilled point, the spatial window is expanded by successive iterations in the direction of greater performance gain. The spatial window grows by repeating the previous steps until no improvement is reached.
			\item The number of analogue situations N1 is then reconsidered and optimized for the current level of analogy.
		\end{enumerate}
		\item A new level of analogy can then be added, based on other variables (such as the moisture index) at chosen pressure levels and hours of the day. The number of analogues for the next level of analogy, N2, is initiated at a chosen value. The procedure starts again from step 2 (calibration of the spatial window and the number of analogues) for the new level. The parameters calibrated on the previous analogue levels are fixed and do not change. 
		\item Finally, the numbers of analogues N1 and N2 for the different levels of analogy are reassessed. This is done iteratively by varying the number of analogues of each level in a systematic way.
	\end{enumerate}

@@

	The improvements of the S1 criterion with the rank of the analogues are summarized in Fig. \ref{fig:changes_S1}, which shows (top) quantiles of the S1 criterion for the conventional method and the MTW and (bottom) quantiles of the relative reduction (meaning improvement) due to the MTW. This confirms that all quantiles were similarly reduced (S1 distributions keep their shape), and that this improvement was constantly increasing from the first to the last analogue (Fig. \ref{fig:changes_S1} bottom).

@@

	After recalibrating, changes in the AM parameters could be observed for both the 2Z and 2Z-2MI methods. Among these, the zonal extent of the spatial windows of the circulation analogy decreased slightly (not shown). More significantly, the optimal number of analogues N1 and N2 increased after introducing the MTW by a considerable magnitude (Table \ref{table:analog_nb}): 25~\% to 83~\% for the 2Z method and 20~\% to 67~\% for the final selection of the 2Z-2MI method. The number of analogues N1 of the first analogy level of the 2Z-2MI method reached three times its previous value for the Visp station (N1=135 instead of 45; Table \ref{table:analog_nb}).

@@

	When using the first reconstructed time series (for the reduced period) based on the proportional distribution (see Sect. \ref{sec:reconstruction}), the AM performance was degraded and was even below the conventional method without MTW (Table \ref{table:disaggregation_proportional} to compare to Fig. \ref{fig:plots_CRPSS_2Z} and \ref{fig:plots_CRPSS_2Z-2MI}).

	For the second approach, the synoptic proxy for the temporal disaggregation of the daily time series had to be identified first. The results are illustrated this time for the Zermatt station. Among the considered moisture variables (see Sect. \ref{sec:reconstruction}), the best proxy was the precipitable water at 45° N and 7.5° E, with a time offset of 6~h (Table \ref{table:proxy_correlations}). Table \ref{table:proxy_CRPSS} presents the CRPSS scores obtained by the disaggregated series using the proxy of precipitable water.

@@

	The introduction of the MTW improved the selection of synoptic analogues. Independently of its impact on the prediction skill for precipitation, or the availability of a predictand time series with sub-daily time step, this improvement has a potential for application on long meteorological archives. For example, when processing forecasts for a target day with synoptic similarity with situations from the past related to extreme weather, even though no precipitation archive is available. Indeed, some of those days with strong precipitation events may be documented, either qualitatively in the daily press or more quantitatively in flood reports. It is thus worth to known that the situation at hand has such analogue in the past. Another possible application is a quality assessment of the selection of analogues on a shorter period, where precipitation data with a high temporal resolution is available. Indeed, if the selection of analogues with the MTW on the long period differ from the selection on the short period, this may point out a sub-optimal forecast. Finally, other predictands might not need sub-daily total values, but point observations (e.g. hail, or extreme wind gusts).

@@

	The MTW was found to improve the skill of the precipitation prediction for both the 2Z and 2Z-2MI methods (Fig. \ref{fig:plots_CRPSS_2Z} and \ref{fig:plots_CRPSS_2Z-2MI}, Sect. \ref{sec:influence_scores}). Moreover, it required no additional predictor. With the introduction of the MTW, the performance loss related to the reduction of the archive length was negated (considering a 25 year archive of sub-daily data; the difference could be higher with a shorter archive). It was in this case of the same magnitude as if the length of the archive doubled. Note, that despite the number of candidate situations being four times higher, the gains seem to be lower than for a quadrupled archive length. The likely reason is that an actual longer archive would contain more atmospheric situations that might have been observed less frequently during a shorter period. Moreover, high correlations between sub-daily circulation patterns are expected. The MTW, therefore, did not create four times as many independent data, but the increase in information was nevertheless substantial. In this regards, a reanalysis dataset with a higher temporal resolution might not improve the performance significantly more than a 6-hourly dataset. In contrast, reducing the MTW to a 12-hour time step might reduce redundancy in the archive, but might also reduce the chance of finding better analogue situations, as circulation patterns can evolve substantially in 12~hours.

@@

	More complex methods with additional levels of analogy and more predictors do increase the performance score, and the MTW could also be applied in these situations, as it is likely to improve the analogy of the atmospheric circulation anyway.

@@

	The MTW improved the prediction for days with heavier precipitation, and should improve the prediction of extremes due to better analogue situations, but also due to possible new extreme values resulting from 24-h totals with a certain time shift. However, even though the distribution of analogue precipitation values should move towards the targeted extreme, providing a better prediction, the MTW itself does not allow to predict extreme events that were not yet observed and are, therefore, not present in the archive. The extremes in AMs can be modelled by, for example, extrapolation of a truncated exponential or gamma distribution fitted to the analogue values \citep{Obled2002}. Another possible approach is by combining AMs with other methods \citep[e.g.][]{Chardon2014}. From this perspective, the MTW might increase the prediction of extremes as it improves the distribution of precipitation values for days with higher precipitation, on which post-treatment techniques rely. However, this goes beyond the scope of the present study.

@@

	An analysis of the selected hours for the geopotential predictor seems to confirm this assumption (Fig. \ref{fig:hours_selection_per_season}). It was found that the new choice of the temporal window in winter, when using the MTW approach, is well balanced between the four options. This means a change of 75~\% of the analogues selected compared to the conventional approach. On the contrary, the days during the summer months had a preference for the initial temporal window (Z500 24~h \& Z1000 12~h), likely due to more pronounced diurnal effects, which reduced the potential for improvement of the criteria. The other seasons were between these two extremes, which is consistent with their respective improvements. This seasonal effect was observed for each station in a very similar way and even with slightly larger amplitude than for Ulrichen.

@@

	After the recalibration of the AMs with the MTW, the optimal analogue numbers were significantly higher than in the original methods (see Sect. \ref{sec:recalibration} and Fig. \ref{table:analog_nb}). As shown in Fig. \ref{fig:changes_S1}, the improvement of the S1 criterion grew along with the rank of the analogue, which shows an accumulation of better analogue situations in the distributions. It seems profitable to widen the selection of analogues in order to also keep some whose rank has increased, as they appear to be relevant to the prediction of the precipitation values. The number of good analogues was globally increased.

	A higher number of analogues generally means, with an archive of fixed length, a poorer analogy. Indeed, when the choice of the predictors or the parameters are improved, leading to a better prediction, the optimal number of analogue situations decreases. However, when the length of the archive increases, the optimal number of analogues increases too for a better performance up to a certain threshold \citep[][]{Bontron2004, Hamill2006a}. The observed increase in the number of analogue situations with the MTW resulted in better performance skills for a given method, as it can be seen as an inflation of the archive. However, if new relevant predictors were added to the method, the number of analogues would then decrease.

@@

	One can question the interest of using moving daily totals when 6-hourly precipitation series can be predicted instead. However, the 6-hourly time series generated by the AM might not represent accurately the intra-daily precipitation distribution (results not shown). In addition, sometimes a resolution finer than the daily time step is not needed and another disaggregation technique may be used afterwards. Finally, when using a reconstructed precipitation archive, the errors in intra-daily precipitation distributions have a smaller impact than 24~h daily totals.

@@

	The considered reanalysis dataset, which is the NCEP/NCAR reanalysis I \citep{Kalnay1996}, is relatively old and has a coarse resolution (2.5\degree). Newer reanalysis datasets could have been used in this study and might have resulted in higher performance scores. However, \cite{BenDaoud2009} showed that the sensitivity of the method to the reanalysis dataset is rather small. This is particularly true for simple AMs that mainly rely on the atmospheric circulation, which is already well defined at a coarser resolution. That might not be the case in more elaborate methods relying on thermodynamic data. A comparative analysis of several reanalysis datasets within the AM is being conducted and will be the topic of a dedicated study.

@@

	The two simple methods assessed to reconstruct precipitation archives (Sect. \ref{sec:reconstruction}) did not result in valuable outputs (Sect. \ref{sec:reconstruction_results}). Indeed, the performance improvement brought by the MTW was lost due to a precipitation archive of poor quality. A slight improvement could be obtained for the second method relying on a proxy variable compared to the proportional distribution method, but it was still relatively small, and most of the benefit of the MTW was lost. A more recent reanalysis archive with more accurate moisture variables might produce better proxies.

@@

	The impact of the MTW on the prediction skill was never assessed before due to the shortcoming of long precipitation series at a sub-daily time step. Here, it was assessed for a 25~year time series with a high temporal resolution. After the introduction of the MTW, the performance scores increased at the same magnitude as if the length of the archive doubled.

@@

	The use of the MTW relies partly on the availability of long precipitation series at a sub-daily time step and with high accuracy. First, these archives of high temporal resolution precipitation data are increasing over time. Another possible source of such archives is the establishment of precipitation reanalysis at a regional scale or the use of reanalysis-driven regional climate models or limited area models over a long period. Even though outputs from these models might be biased or not accurate enough, information regarding the timing of the precipitation events could be useful in disaggregating the station time series. When precipitation data with accurate time distributions are available, the use of a MTW in the AM can be considered for any application and in any context, including operational forecasting or climate-related studies.

	Finally, since long meteorological archives are more and more available, the improvements proposed by the MTW especially for days or sequences of heavy precipitation may be interesting even without long continuous precipitation archives. For example, recent target day may have synoptic similarity with situations from the early twentieth century, for which no continuous daily precipitation archive is available. However, some of those days with strong precipitation events may be documented, either qualitatively in the daily press or more quantitatively in flood reports. Nevertheless, it is worth to known that the situation at hand has such analogue in the far past.

@@

	\begin{figure}[htb]
		\begin{center}
			\includegraphics[width=8.3cm]{figures/figure_map.pdf}
		\end{center}
		\caption{Position of the six weather stations of interest (Ulrichen, Zermatt, Visp, Montana, Sion, and Aigle) in the study area.}
		\label{fig:map}
	\end{figure}

	\begin{figure}[htb]
		\begin{center}
			\includegraphics[width=8.3cm]{figures/illustration_moving_window.pdf}
		\end{center}
		\caption{Illustration of the principle of a moving time window. The target situation is the same for the conventional approach and the MTW, while the candidate situations are four times as many with the MTW. The larger horizontal bars represent the 24~h precipitation totals.}
		\label{fig:principle}
	\end{figure}

	\begin{figure}[htb]
		\begin{center}
			\includegraphics[width=8cm]{figures/illustration_disaggregation.pdf}
		\end{center}
		\caption{Illustration of the generation of 24~h total moving averages by means of a proportional distribution. The colours refer to the corresponding day of the daily time series.}
		\label{fig:illustration_disaggregation}
	\end{figure}

>>>>

	\begin{abstract}
		Analogue methods (AMs) predict local weather variables (predictands), such as precipitation, by means of a statistical relationship with predictors at a synoptic scale. The analogy is generally assessed on gradients of geopotential heights first, in order to sample days with a similar atmospheric circulation. Other predictors, such as moisture variables, can also be added in a successive level of analogy.

		The search for candidate situations for a given target day is usually undertaken by comparing the state of the atmosphere at fixed hours of the day for both the target day and the candidate analogues. The main reason is the use of daily precipitation time series due to the length of their available archives, and the unavailability of equivalent archives at a finer time step. However, it is unlikely for the best analogy to occur at the very same hour, while it may be found with a time shift of some hours as it can occur at a different time of day. In order to assess the potential for finding better analogues at a different hour, a moving time window (MTW) has been introduced.

@@

		However, in order to produce quantitative precipitation predictions the MTW requires sub-daily precipitation time series, which are generally available for a shorter period than daily precipitation archives. Therefore, two simple temporal disaggregation methods were assessed in order to make longer archives usable with the MTW. The assessed approaches were not successful, emphasizing the need to use time series with an appropriate chronology. These should be available in the near future, either by means of growing archives of measurements or by the establishment of regional precipitation reanalysis data at sub-daily time step.

		The use of the MTW in the AM can already be considered now for several applications in different contexts, may it be for operational forecasting or climate-related studies.

@@

	Analogue methods (AMs) are based on the hypothesis that two relatively similar synoptic situations may produce similar local effects \citep{Lorenz1956, Lorenz1969}. They are statistical downscaling methods \citep{Maraun2010} and consist of finding past situations that are similar to the target day of interest in terms of the atmospheric circulation or other synoptic predictors. The local weather variables of interest (predictand) that were observed at the analogue dates are used to construct a probabilistic prediction for the target day \citep{Duband1970, Zorita1999}. Multiple variations of the method exist \citep[a non-exhaustive listing can be found in][]{BenDaoud2016}. The AMs are used for operational precipitation forecasting, either in the context of weather forecasting, flood forecasting, or hydropower production \citep[e.g.,][]{Guilbaud1997, Bontron2005, Hamill2006, Desaint2008a, GarciaHernandez2009b, Bliefernicht2010, Marty2010, Marty2012, Horton2012, Obled2014, Hamill2015, BenDaoud2016}, as well as for precipitation downscaling from a climate perspective \citep[e.g.][]{Radanovics2013, Chardon2014, Dayon2015}. Other applications focus on temperatures \citep{Radinovic1975, Woodcock1980, Kruizinga1983, DelleMonache2013, Caillouet2016}, wind \citep{Gordon1987, DelleMonache2013, DelleMonache2011, Vanvyve2015, Alessandrini2015, Junk2015, Junk2015c}, solar power \citep{Alessandrini2015a, Bessa2015}, snow avalanches \citep{Obled1980, Bolognesi1993}, insolation \citep{Bois1981}, and the trajectories of tropical cyclones \citep{Keenan1981, Sievers2000, Fraedrich2003}.

	The spatial transferability of the method is analysed in \citet{Chardon2014} and \citet{Radanovics2013}. A great advantage of AMs is that they create realistic precipitation patterns, since they are based on observed situations with consistent spatial distribution, as long as the analogue dates chosen for a region are the same. Moreover, they can provide multivariate predictions that are physically consistent \citep{Raynaud2016b}. Their temporal transferability has also been the topic of recent studies for past or future climates \citep{Dayon2015, Caillouet2016}.

@@

	Therefore, due to the availability of long precipitation archives at a daily time step that have no equivalent at a finer resolution, AMs are usually implemented on a daily basis. Consequently, the analogue situations are assessed by comparing predictors at fixed hours of the day. However, it can be expected that the analogy of the synoptic situations does not occur systematically at the same time of the day and that better candidates can be found by shifting to a different hour. With this assumption, a moving time window (MTW) was introduced to allow the search for candidates at different hours of the day. Previous tests showed the benefit, in terms of analogy criterion values, of searching for analogue synoptic situations at a finer time step, but without assessing the impact on the prediction skill \citep{Finet2008}.

@@

	Synoptic-scale variables, used as predictors, were extracted from the NCEP/NCAR reanalysis 1 dataset \citep{Kalnay1996} with a 6-hour temporal resolution, 17 pressure levels, and a spatial resolution of 2.5\degree. This dataset is now relatively old, but it is not expected to affect the conclusions of the present study (see discussion in Sect. \ref{sec:old_reanalysis}).

@@

	The first considered AM is based on the analogy of the atmospheric circulation only \citep[Table \ref{table:method_2Z},][]{Obled2002, Bontron2005}. Searching for analogue situations to a target day starts by a seasonal stratification through a preselection step of the potential candidates for analogy. The restriction is a search for analogue days within a 4-month window centred on the target date for every year of the archive. The similarity of the atmospheric circulation of the target date with every day of the preselection is assessed by processing the \citet{Teweles1954} score (S1) that is a comparison of gradients on geopotential heights over a certain spatial window and at certain hours:

@@

	The moving time window (MTW) technique aims at finding better analogue situations at different hours of the day rather than comparing the predictors at the same fixed hours. If the target situation is kept at 12 and 24~h~UTC for Z1000 and Z500 respectively, candidate situations are not only considered at 12 and 24~h~UTC, but at other hours by allowing a time shift. Therefore, instead of looking for analogues at a 24-h time step, they are sought at the time step matching the predictor temporal resolution which is a 6-h time step in this study (Fig. \ref{fig:principle}).

@@

	In order to assess the benefit of searching for analogue situations at a sub-daily time step for quantitative precipitation prediction, an appropriate precipitation series is required. On the basis of high temporal resolution time series (Sect. \ref{sec:data}), 24-h totals were processed at a 6-hour time step by means of a moving 24-h total. Since sub-daily precipitation time series are available on a shorter period than daily ones, the loss of performance resulting from a reduction of a 47~year archive (1961 to 2008) to 25~years (1982 to 2007) can be expected. However, the competition between the loss of performance due to a smaller archive length and the potentially better analogy between target and MTW candidates needs to be assessed.

@@

	It would be profitable to be able to apply the MTW to a longer archive (here, 1961 to 2008), rather than being limited to the reduced period where the sub-daily precipitation data are available (cf. previous section). Therefore, in order to reconstruct a longer archive of moving 24-h totals, two simple disaggregation approaches of the daily precipitation time series were assessed.

	The first technique was a proportional distribution, where the observed daily precipitations were considered constant during the measuring period (6~h~UTC to 6~h~UTC the next day). Proportional parts of the original daily time series were allocated into a new moving average of 24-h totals (Fig. \ref{fig:illustration_disaggregation}).

@@

		\item For every level of analogy:
		\begin{enumerate}
			\item Identification of the most skilled unitary cell (one point for moisture variables and four for geopotential heights when using the S1 criterion) over a large domain. Every point (or cell) of the full domain is assessed on all predictors of the level of analogy, jointly (consisting generally of the same variable but on different pressure levels and at different hours).
			\item From this most skilled point, the spatial window is expanded by successive iterations in the direction of greater performance gain. The spatial window grows by repeating the previous steps until no improvement is reached.
			\item The number of analogue situations $N_{1}$ is then reconsidered and optimized for the current level of analogy.
		\end{enumerate}
		\item A new level of analogy can then be added, based on other variables (such as the moisture index) at chosen pressure levels and hours of the day. The number of analogues for the next level of analogy, $N_{2}$, is initiated at a chosen value. The procedure starts again from step 2 (calibration of the spatial window and the number of analogues) for the new level. The parameters calibrated on the previous analogue levels are fixed and do not change. 
		\item Finally, the numbers of analogues $N_{1}$ and $N_{2}$ for the different levels of analogy are reassessed. This is done iteratively by varying the number of analogues of each level in a systematic way.
	\end{enumerate}

@@

	The improvements of the analogy with the rank of the analogues are summarized in Fig. \ref{fig:changes_S1}, which shows (top) quantiles of the S1 criterion for the conventional method and the MTW, and (bottom) quantiles of the relative reduction (meaning improvement) due to the MTW. This confirms that all quantiles were similarly reduced (S1 distributions keep their shape), and that this improvement was constantly increasing from the first to the last analogue (Fig. \ref{fig:changes_S1} bottom).

@@

	After recalibrating, changes in the AM parameters could be observed for both the 2Z and 2Z-2MI methods. Among these, the zonal extent of the spatial windows of the circulation analogy decreased slightly (not shown). More significantly, the optimal number of analogues $N_{1}$ and $N_{2}$ increased after introducing the MTW by a considerable magnitude (Table \ref{table:analog_nb}): 25~\% to 83~\% for the 2Z method and 20~\% to 67~\% for the final selection of the 2Z-2MI method. The number of analogues $N_{1}$ of the first analogy level of the 2Z-2MI method reached three times its previous value for the Visp station ($N_{1}$~=~135 instead of 45; Table \ref{table:analog_nb}).

@@

	When using the first reconstructed time series based on the proportional distribution (see Sect. \ref{sec:reconstruction}), the AM performance was degraded and was even below the conventional method without MTW (Table \ref{table:disaggregation_proportional} to compare to Fig. \ref{fig:plots_CRPSS_2Z} and \ref{fig:plots_CRPSS_2Z-2MI}).

	For the second approach, the synoptic proxy for the temporal disaggregation of the daily time series had to be identified first. The results are illustrated this time for the Zermatt station. Among the considered moisture variables (see Sect. \ref{sec:reconstruction}), the best proxy was the precipitable water at 45° N and 7.5° E, with a time offset of -6~h (Table \ref{table:proxy_correlations}). Table \ref{table:proxy_CRPSS} presents the CRPSS scores obtained by the disaggregated series using the proxy of precipitable water which are also lower than the conventional method.

@@

	The introduction of the MTW improved the selection of synoptic analogues. Independently of its impact on the prediction skill for precipitation, or the availability of a predictand time series with sub-daily time step, this improvement has a potential for application on long meteorological archives. For example, when processing forecasts for a target day with synoptic similarity with situations from the past related to extreme weather, even though no precipitation archive is available. Indeed, some of those days with strong precipitation events may be documented, either qualitatively in the daily press or more quantitatively in flood reports. It is thus worth to known that the situation at hand has such analogue in the past. Another possible application is a quality assessment of the selection of analogues on a shorter period, where precipitation data with a high temporal resolution is available. Indeed, if the selection of analogues with the MTW on the long period, for a specific target day, differ from the selection on the short period, this may point out a sub-optimal forecast. Finally, other predictands might not need sub-daily total values, but point observations (e.g. hail, or extreme wind gusts), which make them easier to use with the MTW.

@@

	The MTW was found to improve the skill of the precipitation prediction for both the 2Z and 2Z-2MI methods (Fig. \ref{fig:plots_CRPSS_2Z} and \ref{fig:plots_CRPSS_2Z-2MI}, Sect. \ref{sec:influence_scores}). Moreover, it required no additional predictor. With the introduction of the MTW, the performance loss related to the reduction of the archive length was negated (considering a 25 year archive of sub-daily data; the difference could be higher with a shorter archive). It was in this case of the same magnitude as if the length of the archive doubled. Note, that despite the number of candidate situations being four times as many, the gains seem to be lower than for a quadrupled archive length. The likely reason is that an actual longer archive would contain more atmospheric situations that might have been observed less frequently during a shorter period. Moreover, high correlations between sub-daily circulation patterns are expected. The MTW, therefore, did not create four times as many independent data, but the increase in information was nevertheless substantial. In this regards, a reanalysis dataset with a higher temporal resolution might not improve the performance significantly more than a 6-hourly dataset. In contrast, reducing the MTW to a 12-hour time step might reduce redundancy in the archive, but might also reduce the chance of finding better analogue situations, as circulation patterns can evolve substantially in 12~hours.

@@

@@

	The MTW improved the prediction for days with heavier precipitation, and should improve the prediction of extremes due to better analogue situations, but also due to possible new extreme values resulting from 24-h totals with a certain time shift. However, even though the distribution of analogue precipitation values should move towards the targeted extreme, providing a better prediction, the MTW itself does not allow to predict extreme events that were not yet observed and are, therefore, not present in the archive. The extremes in AMs can be modelled by, for example, extrapolation of a truncated exponential or gamma distribution fitted to the analogue values \citep{Obled2002}. Another possible approach is by combining AMs with other methods \citep[e.g.][]{Chardon2014}. From this perspective, the MTW might improve the prediction of extremes as it improves the distribution of precipitation values for days with higher precipitation, on which post-treatment techniques rely. However, this goes beyond the scope of the present study.

@@

	An analysis of the selected hours for the geopotential height predictor seems to confirm this assumption (Fig. \ref{fig:hours_selection_per_season}). It was found that the new choice of the temporal window in winter, when using the MTW approach, is well balanced between the four options. This means a change of 75~\% of the analogues selected compared to the conventional approach. On the contrary, the days during the summer months had a preference for the initial temporal window (Z500 24~h \& Z1000 12~h), likely due to more pronounced diurnal effects, which reduced the potential for improvement of the criteria. The other seasons were between these two extremes, which is consistent with their respective improvements. This seasonal effect was observed for each station in a very similar way and even with slightly larger amplitude than for Ulrichen.

@@

	After the recalibration of the AMs with the MTW, the optimal analogue numbers were significantly higher than in the original methods (see Sect. \ref{sec:recalibration} and Table \ref{table:analog_nb}). As shown in Fig. \ref{fig:changes_S1}, the improvement of the S1 criterion grew along with the rank of the analogue, which shows an accumulation of better analogue situations in the distributions. It seems profitable to widen the selection of analogues in order to also keep some whose rank has increased, as they appear to be relevant to the prediction of the precipitation values. The number of good analogues was globally increased.

	A higher number of analogues generally means, with an archive of fixed length, a poorer analogy. Indeed, when the choice of the predictors or the parameters are improved, leading to a better prediction, the optimal number of analogue situations decreases. However, when the length of the archive increases, the optimal number of analogues increases too for a better performance up to a certain threshold \citep[][]{Bontron2004, Hamill2006a}. The observed increase in the number of analogue situations with the MTW resulted in better performance skills for the given methods, as it can be seen as an inflation of the archive. However, if new relevant predictors were added to the method, the number of analogues would then decrease.

@@

	One can question the interest of using moving daily totals when 6-hourly precipitation series can be predicted instead. However, the 6-hourly time series generated by the AM might not represent accurately the intra-daily precipitation distribution (results not shown). In addition, sometimes a resolution finer than the daily time step is not needed and another disaggregation technique may be used afterwards. Finally, when using a reconstructed precipitation archive, the errors in intra-daily precipitation distributions have a smaller impact than 24-h daily totals.

@@

	The considered reanalysis dataset, which is the NCEP/NCAR reanalysis 1 \citep{Kalnay1996}, is relatively old and has a coarse resolution (2.5\degree). Newer reanalysis datasets could have been used in this study and might have resulted in higher performance scores. However, \cite{BenDaoud2009} showed that the sensitivity of the method to the reanalysis dataset is rather small. This is particularly true for simple AMs that mainly rely on the atmospheric circulation, which is already well defined at a coarser resolution. That might not be the case in more elaborate methods relying on thermodynamic data. A comparative analysis of several reanalysis datasets within the AM is being conducted and will be the topic of a dedicated study.

@@

	The two simple methods assessed to reconstruct precipitation archives (Sect. \ref{sec:reconstruction}) did not result in valuable outputs (Sect. \ref{sec:reconstruction_results}). Indeed, the performance improvement brought by the MTW was lost due to the poor quality of the precipitation archives. A slight improvement could be obtained for the second method relying on a proxy variable compared to the proportional distribution method, but it was still relatively small, and most of the benefit of the MTW was lost. A more recent reanalysis archive with more accurate moisture variables might produce better proxies.

@@

	The impact of the MTW on the prediction skill was never assessed before due to the shortcoming of long precipitation series at a sub-daily time step. Here, it was assessed for a 25~year time series with a high temporal resolution. After the introduction of the MTW, the performance scores increased of the same magnitude as if the length of the archive doubled.

@@

	The use of the MTW relies partly on the availability of long precipitation series at a sub-daily time step and with high accuracy. First, these archives of high temporal resolution precipitation data are increasing over time. Another possible source of such archives is the establishment of precipitation reanalysis at a regional scale or the use of reanalysis-driven regional climate models or limited area models over a long period. Even though outputs from these models might be biased or not accurate enough, information regarding the timing of the precipitation events could be useful in disaggregating the station time series.

	Finally, since long meteorological archives (reanalysis datasets) are more and more available, the improvements proposed by the MTW especially for days with heavy precipitation may be interesting even without long continuous precipitation archives. For example, recent target day may have synoptic similarity with situations from the early twentieth century, for which no continuous daily precipitation archive is available. However, some of those days with strong precipitation events may be documented, either qualitatively in the daily press or more quantitatively in flood reports. Nevertheless, it is worth to known that the situation at hand has such analogue in the far past.

	The use of the MTW in the AM can already be considered now for several applications in different contexts, may it be for operational forecasting or climate-related studies.

@@

	\begin{figure}[htb]
		\begin{center}
			\includegraphics[width=8.3cm]{figures/figure_map.pdf}
		\end{center}
		\caption{Position of the six weather stations of interest (Ulrichen, Zermatt, Visp, Montana, Sion, and Aigle) in the upper Rh\^{o}ne catchment in Switzerland.}
		\label{fig:map}
	\end{figure}

	\begin{figure}[htb]
		\begin{center}
			\includegraphics[width=8.3cm]{figures/illustration_moving_window.pdf}
		\end{center}
		\caption{Illustration of the principle of a moving time window. The target situation is the same for the conventional approach and the MTW, while the candidate situations are four times as many with the MTW. The larger horizontal bars represent the 24-h precipitation totals.}
		\label{fig:principle}
	\end{figure}

	\begin{figure}[htb]
		\begin{center}
			\includegraphics[width=8cm]{figures/illustration_disaggregation.pdf}
		\end{center}
		\caption{Illustration of the generation of 24-h total moving averages by means of a proportional distribution. The colours refer to the corresponding day of the daily time series.}
		\label{fig:illustration_disaggregation}
	\end{figure}

	\begin{figure}[htb]
		\includegraphics[width=8.3cm]{figures/plots_CRPSS_2Z.pdf}
		\caption{Performance score (CRPSS) of the AM on the atmospheric circulation at the different stations for (dashed) the full archive, i.e. 1961-2008; (yellow) the reduced archive, i.e. 1982-2007; (blue) the introduction of the MTW on the reduced archive; and (green) the recalibrated parameters of the AM with the MTW.}
		\label{fig:plots_CRPSS_2Z}
	\end{figure}
